InteroceptionScale - Data Analysis

### 2024-12-18 study1/analysis/2_analysis.qmd
final

@@

```{r}
#| fig-width: 9
#| fig-height: 8
#| warning: false

@@

ggraph(layout) +
  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
  geom_node_point(aes(color=dimension, shape=level), size=12) +
  geom_node_text(aes(label=name), fontface="bold") +
  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
  scale_color_manual(values=c(
    "Deficit"="#90CAF9", "Awareness"="#C5E1A5", "Sensitivity"="#EF9A9A", 
    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
                     breaks=c("Deficit", "Awareness", "Sensitivity")) +
  theme_void() +
  theme(legend.title = element_text(face="bold")) +
  labs(color="Metaclusters")
```

>>>>

```{r corsimilarity}
#| fig-width: 10
#| fig-height: 10
#| fig-dpi: 200

@@

```{r graph}
#| fig-width: 9
#| fig-height: 8
#| fig-dpi: 200

#| warning: false

@@

ggraph(layout) +
  geom_edge_link(aes(edge_alpha=as.numeric(type == "virtual"), edge_width = abs(link)), edge_width=0.2, color="grey") +
  geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real"))) +
  geom_node_point(aes(color=dimension, shape=level), size=12) +
  geom_node_text(aes(label=name), fontface="bold") +
  # geom_node_text(aes(label = dimmension_label, angle = node_angle(x, y), hjust = 'outward')) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 7), guide="none") +
  scale_edge_colour_gradientn(colors=c("#E53935", "#E53935", "white", "#43A047", "#43A047"), 
                              values=c(-1, -0.5, 0, 0.5, 1), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle"), guide="none") +
  scale_color_manual(values=c(
    "Deficit"="#90CAF9", "Awareness"="#C5E1A5", "Sensitivity"="#EF9A9A", 
    "L1"="#B39DDB", "L9"="#9FA8DA", "L13"="#90CAF9", "L18"="#81D4FA", "L3"="#80DEEA",
    "L4"="#F3F29D", "L6"="#E6EE9C", "L15"="#D6E8A1", "L8"="#C5E1A5", "L10"="#B5DCA6", "L5"="#A5D6A7", "L2"="#93D1B6",
    "L17"="#CE93D8", "L14"="#F48FB1", "L12"="#EF9A9A", "L16"="#FFAB91", "L11"="#FFCC80", "L7"="#FFE082"),
                     breaks=c("Deficit", "Awareness", "Sensitivity")) +
  theme_void() +
  theme(legend.title = element_text(face="bold")) +
  labs(color="Metaclusters")
```
